---
title: "REPORT OF DATA-SCIENCE CLASS"
author: "Santiago Pulido Guerrero"
date: "23-11-2020"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
--- -g 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

## CHAPTER 2: INTRO TO THE TIDYVERSE
#CHALLENGE 1: ANALYSIS OF SALES BY PLACE AND YEAR

Last compiled: `r Sys.Date()`

1) Analysis of the sales by location and by year and location considering the 12 states of Germany and using bar plots.

```{r}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----

# 1.0 Load libraries ----
library(ggplot2)
library(tidyverse)
library(readxl)
library("writexl")

# 2.0 Importing Files ----

bikes_data <- read_excel(path = "D:/data-science/DS_Data-Science/00_data/01_bike_sales/01_raw_data/bikes.xlsx",sheet = NULL)
bikeshops_data <- read_excel(path = "D:/data-science/DS_Data-Science/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx",sheet = NULL)
orderlines_data <- read_excel(path = "D:/data-science/DS_Data-Science/00_data/01_bike_sales/01_raw_data/orderlines.xlsx",sheet = NULL)

# 3.0 Joining Data ----

bikes_total_dataA = left_join(orderlines_data,bikes_data, by = c("product.id"="bike.id"))
bikes_total_dataB = left_join(orderlines_data,bikeshops_data, by = c("customer.id"="bikeshop.id"))
bike_orderlines_wrangled = left_join(bikes_total_dataA,bikes_total_dataB,by = NULL)

# 5.0 Wrangling Data ----

bike_orderlines_wrangled_tbl <- bike_orderlines_wrangled %>% separate(col = 'location',into = c("City","State"),sep = ",")%>% 
mutate(total.price = price*quantity)%>%
select(order.id, contains("order"),contains("model"),contains("location"),price, quantity, total.price,everything()) %>%
rename(bikeshop = name) %>%  set_names(names(.) %>% str_replace_all("\\.", "_"))


# 6.0 Business Insights ----

# 6.1 States with the highest revenue ----

# Step 1 - Manipulate

sales_by_loc_tbl <- bike_orderlines_wrangled_tbl %>% separate(col = "order_date",into = c("order_year","order_month","order_day"),sep = "-") %>% 
  group_by(State) %>%  summarize(total_sales = sum(total_price))%>%
  mutate(sales_in_euros = scales::dollar(total_sales, big.mark = ".",decimal.mark = ",",prefix = "",suffix = "\u20ac"))

sales_by_loc_year_tbl <- bike_orderlines_wrangled_tbl %>% separate(col = "order_date",into = c("order_year","order_month","order_day"),sep = "-") %>% 
  group_by(order_year,State) %>%  summarize(total_sales = sum(total_price))%>%
  mutate(sales_in_euros = scales::dollar(total_sales, big.mark = ".",decimal.mark = ",",prefix = "",suffix = "\u20ac"))
  
# Step 2 - Visualize

sales_by_loc_tbl %>% ggplot(aes(x = State,y = total_sales))+ theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
geom_col(fill = "#2DC6D6") + geom_label(aes(label = sales_in_euros)) + geom_smooth(method = "lm", se = FALSE) +
scale_y_continuous(labels = scales::dollar_format(big.mark = ".",decimal.mark = ",",prefix = "",suffix = "\u20ac")) +  
labs(
    title    = "Revenue by state",
    subtitle = "Highest revenues",
    x = "", # Override defaults for x and y
    y = "Revenue in euros \u20ac"
  )
ggsave("sales_by_loc_tbl.png", height = 30, width = 35,units = "cm")

# 6.2 Sales by Year and Category 2 ----

# Step 2 - Visualize

sales_by_loc_year_tbl %>% ggplot(aes(x = order_year,y = total_sales, fill = State))+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  geom_col() + facet_wrap(~ State) + scale_y_continuous(labels = scales::dollar_format(big.mark = ".",decimal.mark = ",",prefix = "",suffix = "\u20ac")) +  
  labs(
    title    = "Revenue by state",
    subtitle = "Highest revenues",
    fill = "Sales by states"
  )
ggsave("sales_by_loc_year_tbl.png", height = 35, width = 35,units = "cm")

# 7.0 Writing Files ----

#install.packages("writexl")
library("writexl")
# 7.1 XLSX ----
sales_by_loc_tbl %>% write_xlsx("D:/data-science/DS_Data-Science/00_data/01_bike_sales/02_wrangled_data/sales_by_loc.xlsx")
sales_by_loc_year_tbl %>% write_xlsx("D:/data-science/DS_Data-Science/00_data/01_bike_sales/02_wrangled_data/sales_by_loc_year.xlsx")
# 7.2 CSV ----
sales_by_loc_tbl %>% write_csv("D:/data-science/DS_Data-Science/00_data/01_bike_sales/02_wrangled_data/sales_by_loc.csv")
sales_by_loc_year_tbl %>% write_csv("D:/data-science/DS_Data-Science/00_data/01_bike_sales/02_wrangled_data/sales_by_loc_year.csv")
# 7.3 RDS ----
sales_by_loc_tbl %>% write_rds("D:/data-science/DS_Data-Science/00_data/01_bike_sales/02_wrangled_data/sales_by_loc.rds")
sales_by_loc_year_tbl %>% write_rds("D:/data-science/DS_Data-Science/00_data/01_bike_sales/02_wrangled_data/sales_by_loc_year.rds")
```

# CHALLENGE 2: 
## API data acquisition
For the API data acquisition challenge, the OPENWEATHERMAP provider was selected. The code used was

```{r,message=FALSE}
## CHALLENGE 2.0
# SECTION 1.0
# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(glue)      # String interpolation
library(httr)      # API GET function
library(rstudioapi) # Securing credentials

# 1.2 request data from source

city_name <- list("Hamburg","Tokio","Bogota")
Api_key <- "d7736dd80cd838bf45d50b696167e9f5"
city_wheather = list()
x = c()
n = 0;
for (i in city_name){
n = n + 1
resp <- GET(glue("https://api.openweathermap.org/data/2.5/weather?q={i}&units=metric&appid={Api_key}"));
x[n] <- content(resp, as = "text")

}

```

```{r}
# 1.3 Print data from the Source
map(x,print);

# API Key protection

alphavantage_api_url <- "https://www.alphavantage.co/query"
ticker               <- "WDI.DE"

GET(alphavantage_api_url, query = list('function' = "GLOBAL_QUOTE",
                                       symbol     = ticker,
                                       apikey     = Sys.getenv("MyPersonalToken"))
)

```

## Scraping information

The selected competitor website was https://www.rosebikes.de/. The code produced is

```{r}

# SECTION 2.0

# 2.0 LIBRARIES

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(httr)      # include functions 
library(rstudioapi)# Securing credentials
# 2.1 Collection of products features

url_home <- "https://www.rosebikes.de/fahrräder/mtb"

xopen(url_home)

html_home <- read_html(url_home)

mtb_bikes_family <- html_home %>%
  
  html_nodes(css = ".catalog-category-bikes__title-text") %>% html_text() %>% 
  
  enframe(name = "position",value = "Family_class") %>% mutate( family_class = str_glue("#MTB"))
  
  
mtb_bikes_price <- html_home  %>% html_nodes(css = ".catalog-category-bikes__price-title") %>% html_text() %>% 
  
  enframe(name = "position",value = "Price") 

mtb_bikes_tbl <- mtb_bikes_family %>% left_join(mtb_bikes_price, by = c("position"="position"))

# Printing the data

mtb_bikes_tbl %>% print()

alphavantage_api_url <- "https://www.alphavantage.co/query"
ticker               <- "WDI.DE"

GET(alphavantage_api_url, query = list('function' = "GLOBAL_QUOTE",
                                       symbol     = ticker,
                                       apikey     = Sys.getenv("MyPersonalToken"))
)

```
# CHALLENGE 3

## Part 1

The top ten companies with the most patents

```{r eval = FALSE}

# 1.0 libraries
library(vroom)
library(readxl)
library("writexl")
library(tidyr)
library(purrr)
library("stringr") 
library(dplyr)
library(data.table)
# Tidyverse
library(tidyverse)

# 2.0 import data

col_assignee <- list(
  id = col_character(),
  type = col_character(),
  name_first = col_character(),
  name_last = col_character(),
  organization = col_character()
)

col_patent_assignee <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_character()
  
)

library(vroom)
col_types <- list(
  id = col_character(),
  type = col_character(),
  number = col_character(),
  country = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double()
)

uspc_tbl <- list(
  uuid = col_character(),
  pat_id = col_character(),
  mainclass_id = col_character(),
  subclass_id = col_character(),
  sequence = col_character()
)

patent_tbl <- vroom(
  file       = "patent.tsv", 
  delim      = "\t", 
  col_types  = list(id = col_skip(),type = col_skip(),abstract = col_skip(),withdrawn = col_skip()),
  na         = c("", "NA", "NULL")
)

assignee_tbl <- vroom(
  
  file = "assignee.tsv",
  delim      = "\t", 
  col_types  = list(name_first = col_skip(),name_last = col_skip()),
  na         = c("", "NA", "NULL")
  
)

patent_assignee_tbl <- vroom(
  
  file = "patent_assignee.tsv",
  delim      = "\t", 
  col_types  =  col_patent_assignee,
  na         = c("", "NA", "NULL")
  
)

uspc_tbl <- vroom(
  
  file = "uspc.tsv",
  delim      = "\t", 
  col_types  =  list(uuid = col_skip(), subclass_id = col_skip()),
  na         = c("", "NA", "NULL")
  
)


class(uspc_tbl)

setDT(uspc_tbl)

class(patent_tbl)

setDT(patent_tbl)

class(assignee_tbl)

setDT(assignee_tbl)

class(patent_assignee_tbl)

setDT(patent_assignee_tbl)

## Challenge 3.1

### 3.0 Data Wranggling

patent_assignee_tbl <- patent_assignee_tbl %>% select(patent_id, assignee_id, location_id) %>% rename(pat_id = patent_id,
                                                                                                      id = assignee_id,
                                                                                                      Loc_id = location_id) 

complete_patent_tbl <- merge(x = patent_assignee_tbl, y = assignee_tbl, by = "id",all.x = TRUE, all.y = TRUE)

### filtering Critirea

## Categories

### 2 US Company or Corporation
### 4 US individual
### 6 US Federal government
### 8 US County Government
### 9 US State Government

filtered_data <- complete_patent_tbl %>% select(type,organization) %>% filter((type %% 2 == 0)|(type == 9))

num_patents_by_co <- filtered_data %>% group_by(organization) %>% count() %>% arrange(desc(n)) 

num_patents_by_co %>% head(n=10)

```

```{r}
library(readxl)

num_patents_by_comp <- read_csv("num_patents_by_com.csv")

num_patents_by_comp 
```

```{r eval = FALSE}

## Challenge 3.2
patent_assignee_tbl <- complete_patent_tbl %>% select(id,pat_id,Loc_id,type,organization)%>% rename(id = id,
                                                                                                    number = pat_id,
                                                                                                    loc_id = Loc_id,
                                                                                                    type = type,
                                                                                                    org = organization)

merged_patent_tbl <- merge(x = patent_tbl, y = patent_assignee_tbl, by = "number",all.x = TRUE, all.y = TRUE)


filtered_patent_tbl <- merged_patent_tbl %>% select(number,country,date,type,org) %>% filter((type %% 2 == 0)|(type == 9))

filtered_patent_tbl <- filtered_patent_tbl %>% select(number,country,date,type,org)  %>% filter(!is.na(date)) 

ru_patent_tbl <- filtered_patent_tbl %>% select(number,country,date,org) %>% separate(col = date,
                                                                   into = c("year","month","day"),
                                                                   sep = '-',remove = FALSE)
ru_patent_tbl <- ru_patent_tbl %>% select(-date)

ru_patent_tbl <- ru_patent_tbl %>% select(number,country,year,org) %>% filter(year == 2019)

patents_by_company_in_2019 <- ru_patent_tbl %>% group_by(org,year) %>% count() %>% arrange(desc(n)) 

patents_by_company_in_2019 %>% head(n=10)

```

```{r}
patents_by_company_2019 <- read_csv("patents_by_company_2019.csv")

patents_by_company_2019 

``` 

```{r eval = FALSE}

complete_upatent_tbl <- complete_patent_tbl %>% select(id,pat_id,Loc_id,type,organization) %>% filter(!is.na(pat_id)) %>% arrange(desc(pat_id))

uspc_tbl <- uspc_tbl %>% select(patent_id,mainclass_id,sequence) %>% rename(pat_id = patent_id,
                                                                            mclass = mainclass_id,
                                                                            sqc = sequence)

complete_upatent_tbl <- merge(x = complete_upatent_tbl, y = uspc_tbl, by = "pat_id",all.x = TRUE, all.y = TRUE) %>% filter(!is.na(mclass))

complete_upatent_tbl <- complete_upatent_tbl %>% filter(!is.na(organization))

filtered_patent_tbl <- complete_upatent_tbl %>% group_by(pat_id,organization,mclass) %>% count() %>% arrange(desc(n))

top_10_companies <- filtered_patent_tbl %>% group_by(pat_id,organization) %>% count() %>% arrange(desc(n))

top_10_org <- top_10_companies %>%  group_by(organization) %>% count() %>% arrange(desc(n)) %>% head(n=10)

top_uspto <- merge(x = top_10_org, y = filtered_patent_tbl, by = "organization",all.x = TRUE, all.y = TRUE)

top_5_uspto <- top_uspto %>% select(organization, n.x, pat_id, mclass) %>% filter(!is.na(n.x)) %>% arrange(desc(mclass))

top_5_uspto <- top_5_uspto %>% group_by(mclass) %>% count() %>% arrange(desc(n))

top_5_uspto %>% head(n = 5) %>% glimpse() 

## filtering Critirea

## Step 1:
###       a) Trew away the na.rows of organization and mclass at the frist two command lines
###       b) Counted the number of times a patent was assigned to an organization, considering the mainclass
###       c) Counted the number of times an organization was awarded a patent
###       d) Extracted the top ten companies with most patents in top_10_org
###       e) Filtered (using merge) the top ten companies in the filtered_patent_tbl to get the the mainclass of the top tehn companies
###       f) Finally, count the number of times mainclasses appears from the top ten companies
###       h) Got the top five USPTO tech mainclasses
```

```{r}

top_5_uspto <- read_csv("top_5_uspto.csv")

top_5_uspto 

```

## Challenge 4 
### COVID confirmed cases


```{r}
# Challenge 1

# 1.0 Libraries
library(tidyverse)
library(lubridate)
library(readxl)

# 2.0 Data acquisition

covid_data_tbl <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")

# 3.0 Data manipulation

cases_in_2020 <- covid_data_tbl %>% select(dateRep,year,month,cases,countriesAndTerritories,continentExp) %>% 
  mutate(across(countriesAndTerritories, str_replace_all, "_", " ")) %>%
  mutate(countriesAndTerritories = case_when(
    
    countriesAndTerritories == "United Kingdom" ~ "UK",
    countriesAndTerritories == "United States of America" ~ "USA",
    countriesAndTerritories == "Czechia" ~ "Czech Republic",
    TRUE ~ countriesAndTerritories
    
  ))

cases_by_dmonth_2020 <- cases_in_2020 %>% select(dateRep,month,year,cases,countriesAndTerritories) %>%
  mutate(dateRep = dmy(dateRep)) %>% filter(year %in% "2020" & countriesAndTerritories %in% c("Germany","France","UK","Spain","USA")) %>%
  arrange((dateRep))

cases_by_month_2020 <- cases_by_dmonth_2020 %>% group_by(countriesAndTerritories) %>%
  mutate(cumulative_cases = cumsum(cases)) %>% ungroup()
  
cases_by_month_2020 %>% ggplot(aes(x = dateRep,y = cumulative_cases,size = total_cases)) + 
  geom_line(aes(color = countriesAndTerritories), size = 1.0) +
  scale_x_date(breaks = "1 month", date_labels = "%B") + 
  scale_y_continuous(labels = scales::number_format(scale = 1/1e6, big.mark = ".", decimal.mark = ",", suffix = "M"))+
  theme_test()+theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(
    title = "COVID-19 confirmed cases worldwide",
    subtitle = "Last update: 30-11-2020",
    caption = "Data taken from: https://opendata.ecdc.europa.eu/covid19/casedistribution/csv",
    x = "Months",
    y = "Cumulative cases",
    color = "Countries"
    
  ) 
  
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.